Assessment of the KLGO Coastal Waterbird Survey Monitoring Program

### 2019-02-09 analysis/paper/paper.Rmd
Separated functionality in 'data_exploration.R' into a 'data_wrangling' script and a 'survey_timing' data visualization script. Modifications to r code chunks to get knitr to compile to html, word, or pdf.

# Issues to Resolve
- why isn't code chunk option warning= FALSE suppressing warnings() in Data_Retrieval? (from read_csv)
- How do we use latex figure environment in rmarkdown (for inclusion of ggplot graphics; captioning figures and labelling for cross-references, etc)?
- conversion from paper.md to paper.pdf (pandoc issue?) (i) update MikTex package, set dev=c('pdf') in setup
- github permissions for Madeleine on local machine
- What is up with 2008 surveys? why such distinct timing?

>>>>

# Issues to Resolve
- How do we use latex figure environment in rmarkdown (for inclusion of ggplot graphics; captioning figures and labelling for cross-references, etc)?
- conversion from paper.md to paper.pdf (pandoc issue?) 
  (i) update MikTex package, set dev=c('pdf') in setup
- github permissions for Madeleine on local machine
- adding files to .gitignore
- What is up with 2008 surveys? why such distinct timing?
